### 2020-12-15 Supplement_forThesis.Rmd
preparing to submit to ZOoScripta - getting word docs for dissertation

---
bibliography: manuscript.bib
csl: pnas.csl
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_document2:
    toc: FALSE
indent: TRUE
monofont: "Times New Roman"
fontsize: 12pt
language:
  label:
    fig: "**Figure S**"
    tab: "**Table S**"
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage{placeins}
---

>>>>

---
bibliography: manuscript.bib
csl: pnas.csl
site: "bookdown::bookdown_site"
output:
  bookdown::word_document2:
    toc: FALSE
indent: TRUE
monofont: "Times New Roman"
fontsize: 12pt
language:
  label:
    fig: "**Figure S**"
    tab: "**Table S**"
header-includes:
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage{placeins}
---
